### 2024-06-25 acronyms/acronyms.tex
p2x
nwr
acronym
acronyms
des
nwtrb
nwn

>>>>

\newacronym{p2x}{P2X}{Power-to-X}
\newacronym{nwr}{NWRPO}{Nuclear Waste Repository Project Office}
\newacronym{aul}{AULG}{Affected Unit of Local Government}
\newacronym{osc}{OSCM}{Office of Standard Contract Management}
\newacronym{mrm}{mrem}{millirem}
\newacronym{can}{CANT}{Citizens Against Nuclear Trash}
\newacronym{kmp}{KMP}{Key Measurement Point}
\newacronym{nwb}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{nwn}{NWN}{Office of the Nuclear Waste Negotiator}
